Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-26 files/Chapter3/dynamicconvergence.tex
Chapter 3

Recall that $u^h(t) = \sum_{k} u_k(t)\phi_k$ where $\bar{u}_k = \left( u_1(t), u_2(t), ...  , u_n(t)\right)$.

@@

\newtheorem{DC_Prop2}{Proposition}
\begin{DC_Prop2}
	If $F\in C(J)$, then Problem ODE has a unique solution for each pair of vectors $\bar{u}^h_0$ and $\bar{u}^h_1$
\end{DC_Prop2}

\newtheorem{DC_Prop3}[DC_Prop2]{Proposition}
\begin{DC_Prop3}
	Suppose $M, K, C, F,{u}_0$ and ${u}_1$ are defined as above. Then, the function $u_{h}$ is a solution of Problem GVar$^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
\end{DC_Prop3}

@@

Consider the time interval $J = [0,T]$. Divide $J$ into $N$ steps with length $\tau = \frac{T}{N}$. Each interval can be expressed as $[t_{k-1}, \ t_k]$ for $k = 1,...,N$. Denote the approximation of $u_h$ on the interval $[t_{k-1}, \ t_k]$ by $u_k^h$, i.e. $u_h(t_k) = u_k^h$ for each $k$. (Recall that $u_h(t) = \sum u_i(t)\phi_i$.) A finite difference method is used to compute $u^h_k$ for each $k$.

@@

\vspace*{40mm}

The error $e$, can now be expressed as
\begin{eqnarray}
	e(t_k) = u(t_k) - u^h_k & = & [u(t_k)-u_h(t_k)] + [u_h(t_k) - u^h_k]. \label{error_e}
\end{eqnarray}

@@

From Theorem 2 of the semi-discrete problem an error estimate for
$e_k = [u(t_k)-u_h(t_k)]$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $e_k = [u_h(t_k) - u^h_k]$.

Since the dimension of $S^h$ is not fixed, the equivalence of norms
cannot be used, and therefore this error estimate for $e_k = [u_h(t_k) - u^h_k]$
should also be with respect to the norm of $W$.

A stability result is derived in \cite{BV13}.

@@

Using this lemma, \cite{BV13} prove the error estimate.

\newtheorem*{DC_Thm5_1}{Theorem 2}
\begin{DC_Thm5_1}
	{Main Result}\\
	If $f\in C^{2}([0,T],X)$, then
	\begin{eqnarray*}
		\Vert u(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & K\tau^2
	\end{eqnarray*}
	for each $t\in(0,\ T)$.
\end{DC_Thm5_1}

Recall that $\displaystyle \tau = \frac{T}{N}$. The error estimate for the term
$[u_h(t_k) - u^h_k]$ with respect to the norm of $W$ as proven by the authors
of \cite{BV13} is presented here as Theorem 3.

Finally, Theorem 2 of the semi-discrete problem and Theorem 3 of the fully
discrete problem gives an error estimate for the error $e(t)$. Consequently,
the error estimate $e^h(t) = u(t) - u^h(t)$ is obtained.

\subsection{Main result}
The main result proving the convergence of the solution of the Galerkin
Approximation is given in \cite{BV13} as follows.
\newtheorem*{DC_Thm5}{Theorem 2}
\begin{DC_Thm5}
	{Main Result}\\
	If $f\in C^{2}([0,T],X)$, then
	\begin{eqnarray*}
		\Vert u(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & K\tau^2
	\end{eqnarray*}
	for each $t\in(0,\ T)$.
\end{DC_Thm5}

The constant $K$ depend on $u_h$ and its derivatives.

>>>>

Recall that $u^h(t) = \sum_{k} u_k(t)\phi_k$ where $\bar{u}_k = \left( u_1(t), u_2(t), ...  , u_n(t)\right)$ where each $\phi_k$ corresponds to a node number $k$. More complex cases are treated in Chapter \ref{ch:finite-element-method}.

@@

\newtheorem{DC_Prop2}{Proposition}
\begin{DC_Prop2}
	If $F\in C(J)$, then Problem ODE has a unique solution for each pair of vectors $\bar{u}_0$ and $\bar{u}_1$
\end{DC_Prop2}

\newtheorem{DC_Prop3}[DC_Prop2]{Proposition}
\begin{DC_Prop3}
	Suppose $M, K, C, F,\bar{u}_0$ and $\bar{u}_1$ are defined as above. Then, the function $u_{h}$ is a solution of Problem GVar$^{h}$ if and only if the function $\bar{u}$ is a solution of Problem ODE.
\end{DC_Prop3}

@@

Consider the time interval $J = [0,T]$. Divide $J$ into $N$ steps with length $\tau = \frac{T}{N}$. Each interval can be expressed as $[t_{k-1}, \ t_k]$ for $k = 1,...,N$. Denote the approximation of $u_h$ on the interval $[t_{k-1}, \ t_k]$ by $u_k^h$, i.e. $u_h(t_k)$ corresponds to $u_k^h$ for each $k$. (Recall that $u_h(t) = \sum u_i(t)\phi_i$.) A finite difference method is used to compute $u^h_k$ for each $k$.

@@

In \cite{BV13} it is assumed that there exists a subspace $H$ of $V$ and a positive integer $\alpha$ such that
\begin{eqnarray*}
	\inf_{v\in S^{h}}\Vert w-v\Vert_{V}\leq{C}h^{\alpha}|||w|||_{H},
\end{eqnarray*} for each $w \in H$ where $|||w|||_H$ is a norm or semi-norm for $H$.

\newtheorem*{DC_Thm6_1}{Theorem 2}
\begin{DC_Thm6_1}
	If $u(t) \in H$ and $u'(t) \in H$ for each $t$, then
	\begin{eqnarray*}
		||e^h(t)||_W & \leq & C h^\alpha \left( |||u(t)||_H + |||u'(t)||_H \right),
	\end{eqnarray*} for each $t$.
\end{DC_Thm6_1}

From Theorem 2 for the semi-discrete problem an error estimate for
$e(t) = [u(t)-u_h(t)]$ with respect to the norm of $W$ was obtained. The authors of \cite{BV13} then proceed to obtain an error estimate for $e_k = [u_h(t_k) - u^h_k]$.

The error can then be expressed as
\begin{eqnarray}
	e(t_k) = u(t_k) - u^h_k & = & [u(t_k)-u_h(t_k)] + [u_h(t_k) - u^h_k]. \label{error_e}
\end{eqnarray}

@@

Since the dimension of $S^h$ is not fixed, the equivalence of norms
cannot be used, and therefore this error estimate for $e_k = [u_h(t_k) - u^h_k]$
should also be with respect to the norm of $W$. The local error $e_1$ can be estimated using Taylor polynomials, but then $e_k$ `grows' as $k$ increases.

A stability result is derived in \cite{BV13}. Recall that $\displaystyle \tau = \frac{T}{N}$.

@@

Using this lemma, \cite{BV13} prove the error estimate. The error estimate for the term $[u_h(t_k) - u^h_k]$ with respect to the norm of $W$ as proven by the authors of \cite{BV13} is presented here as Theorem 3.

\newtheorem*{DC_Thm5_1}{Theorem 3}
\begin{DC_Thm5_1}
	If $f\in C^{2}([0,T],X)$, then
	\begin{eqnarray*}
		\Vert u(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & K\tau^2
	\end{eqnarray*}
	for each $t\in(0,\ T)$.
\end{DC_Thm5_1}

\subsection{Main result}
Finally, Theorem 2 of the semi-discrete problem and Theorem 3 of the fully
discrete problem gives an error estimate for the error $e(t)$. Consequently,
the error estimate $e^h(t) = u(t) - u^h(t)$ is obtained.

The main result proving the convergence of the solution of the Galerkin
Approximation is given in \cite{BV13} as follows.
\newtheorem*{DC_Thm5}{Theorem 4}
\begin{DC_Thm5}
	{Main Result}\\
	If $f\in C^{2}([0,T],X)$, then
	\begin{eqnarray*}
		\Vert u(t_{k})-u_{k}^{h}\Vert_{W}\ & \leq & K\tau^2
	\end{eqnarray*}
	for each $t\in(0,\ T)$.
\end{DC_Thm5}

The constant $K$ depend on $u$, $u_h$ and their derivatives.
